Determination of the \ce{^{64}Zn},\ce{^{47}Ti}(n,p) Cross-Sections using a DD Neutron Generator for Medical Isotope Studies

### 2017-02-28 First_np_Paper/first_np_paper.tex
Updated section 2.7 with Lee edits

After irradiation, the co-loaded targets in each experiment were removed from the HFNG and transferred to a counting lab, where their induced activities could be measured via gamma ray spectroscopy. Two detectors were used in this measurement: an Ortec 80\% High-Purity Germanium (HPGe) detector (calibrated from 50 keV - 3800 keV) used for the detection of the higher-energy gamma rays in the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} experiments, and an Ortec planar Low-Energy Photon Spectrometer (LEPS) detector (calibrated from 15 keV - 450 keV) used for the detection of the lower-energy gamma rays in the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} experiments. These can be seen in \autoref{fig:hpge_a} and \autoref{fig:hpge_b}. Both detectors were calibrated for both energy and efficiency, using \ce{^{133}Ba}, \ce{^{137}Cs}, and \ce{^{152}Eu} sources at various distances from the front face of each detector. These efficiencies, along with gamma ray intensities for each transition, are used to convert the integrated counts in each gamma ray photopeak into an activity for the activated isotopes and isomeric states.

\begin{figure*}[H]
    \centering
    \begin{subfigure}[t]{0.7\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \includegraphics[height=2.8in]{./figures/IMG_20160531_182618557_HDR.jpg}
        \caption{ Ortec 80\% HPGe detector}
        \label{fig:hpge_a}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.28\textwidth}
        \centering
%         \includegraphics[width=\textwidth]{./figures/target2.png}
        \includegraphics[height=2.8in]{./figures/IMG_20160531_182635712_HDR.jpg}
        \caption{Ortec planar LEPS detector}
                \label{fig:hpge_b}
    \end{subfigure}
    \caption{High-Purity Germanium Detectors used for gamma spectroscopy of the activated foils.}
     \label{fig:main_ge_detectors}
\end{figure*}

\comment{Does \autoref{fig:main_ge_detectors} serve any purpose? Should it be cut?}

The foils were counted in their polyethylene holder, and placed close to the front face of the detector in use, with the target foil (zinc or titanium) facing towards the front face of the detector when both target and monitor foils were counted simultaneously. This position allows for the detectors to subtend the largest possible solid angle of the gamma rays emitted by the foils. All data collection was performed using the Ortec MAESTRO software. For each experiment the detector dead time was verified to be less than 5\%, to avoid coincidence summing effects. This was never an issue for any experiments, but had it been, the foils would be moved to a position of greater standoff from the detector, to reduce the dead time.  For the  \ce{^{47}Sc} production experiments, the foils were counted simultaneously using a planar LEPS detector. For the \ce{^{64}Cu} production experiments, the Indium foil was first counted separately using an 80\% HPGe detector, to capture the short-lived Indium activities. This is due to the fact that the \ce{^{115}In} can undergo the \ce{^{115}In}(n,$\gamma$)\ce{^{116}In} reaction, with a cross section of 83 mb for 2.76 MeV neutrons. \ce{^{116}In} has a 54 minute half-life, decaying via $\beta^-$ with a Q value of 3.278 MeV. This decay populates several states in \ce{^{116}Sn} capable of emitting gamma rays with $E_\gamma > 2 \times$ the 511-keV gamma, which is produced via pair production in the detector crystal, contaminating the 511-keV channel used to monitor  \ce{^{64}Cu} production. After approximately 4 hours of spectra collection, the activated zinc foil was added back and counting resumed simultaneously with the indium foil. This allowed for decay of nearly all \ce{^{116}In}, avoiding significant 511 keV contamination. Example spectra for each production pathway can be seen in \autoref{fig:spectra_a} and \autoref{fig:spectra_b}.

\begin{figure*}[H]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \includegraphics[width=5in]{./figures/ti_foils.png}
        \includegraphics[width=5in]{./figures/47sc_gspectrum_alt.pdf}
        \caption{ Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a planar LEPS detector}
        \label{fig:spectra_a}
    \end{subfigure}%
    \\
    \begin{subfigure}[t]{\textwidth}
        \centering
%         \includegraphics[width=\textwidth]{./figures/target2.png}
%         \includegraphics[width=5in]{./figures/Sample_spectra.png}
        \includegraphics[width=5in]{./figures/64Cu_gspectrum_alt.pdf}
        \caption{Gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
                \label{fig:spectra_b}
    \end{subfigure}
    \caption{Example gamma spectra collected to monitor radioisotope production.}
     \label{fig:main_spectra}
\end{figure*}

\comment{Example spectra are messy - being updated...}

To verify that each peak corresponds to the assigned transitions, spectra were acquired in a sequence of 15 - 30 minute intervals. By plotting the background-subtracted photopeak counts for a particular channel as a function of time, an exponential decay function may be fit to it, to determine the half-life of the transition in question. Plots of these curves for each transition in this work are seen in Figures \ref{fig:decay_curve_336} - \ref{fig:decay_curve_511}. The fitted functions for each transition agree (at the 1$\sigma$ confidence level) with accepted half-lives from the ENSDF library, confirming the respective peak assignments.

\comment{Reference original ENSDF papers?}

@@

\comment{Need to update \autoref{fig:decay_curves} - figures are blurry}

The background-subtracted integrated counts in each photopeak, as well as the counting duration for each experiment, are tabulated in \autoref{tab:peak_counts}.

@@

@@

Gamma spectroscopy analysis on the several days of collected spectra was used to measure the background-subtracted counts under each of the photopeaks of interest for the induced activities, as described in \autoref{sec:spectroscopy}. For a thin target consisting of \(N_T\) target nuclei, subjected to a constant monoenergetic neutron flux $\phi\pp{\bar{E}}$, the rate of production of the product nucleus will be:

@@

for a reaction with cross-section  $\sigma\pp{\bar{E}}$ at effective energy $\bar{E}$. If this irradiation lasts for  some time $t_1$, and gamma ray spectroscopy of the activated samples begins at a later time $t_2$ and ends at an even later time $t_3$, then the number of product decays (with decay constant $\lambda$) which take place between $t_2$ and $t_3$ will be:

\begin{equation}
\begin{aligned}
D &= \dfrac{R}{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_2} - e^{-\lambda t_3}}
\\
&= \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_2} - e^{-\lambda t_3}} 
\end{aligned}
\end{equation}

If this decay emits a gamma ray with branching ratio $I_\gamma$ photons emitted per decay, and is detected with an absolute efficiency (photons detected / photons emitted) of $\epsilon_\gamma$, then the number of observed decays between $t_2$ and $t_3$ will be:

@@

\begin{align}
N_{obs} &= D \epsilon_\gamma I_\gamma \\
&=  \epsilon_\gamma I_\gamma  \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_2} - e^{-\lambda t_3}} \nonumber
\end{align}

Rearranging in terms of the observed cross-section:

\begin{equation}
\sigma\pp{\bar{E}} = \dfrac{N_{obs}\lambda}{N_T \epsilon_\gamma I_\gamma  \phi\pp{\bar{E}}  \pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_2} - e^{-\lambda t_3}}}
\end{equation}

This model, in which subscripts $P$ indicate a quantity for either the \ce{^{64}Cu} or \ce{^{47}Sc} product, subscripts $In$ indicate a quantity for either the \ce{^{113m}In} or \ce{^{115m}In} isomer, can be taken in ratio, to calculate the measured \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production cross sections, relative to the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering cross sections. Adding in a correction for the small self-attenuation of the gamma rays emitted by the activated foils, the final ratio model can be seen in \autoref{eqn:calc_eqn}:

\begin{align}\label{eqn:calc_eqn}
\sigma_P &= \sigma_{In} \dfrac{A_P}{A_{In}} \dfrac{N_{T,In}}{N_{T,P}} \dfrac{\lambda_P}{\lambda_{In}} \dfrac{e^{\lambda_{In}t_1}-1}{e^{\lambda_{P}t_1}-1}  \\
&\times \dfrac{e^{-\lambda_{In}t_2}-e^{-\lambda_{In}t_3}}{e^{-\lambda_{P}t_2} - e^{-\lambda_{P}t_3}} \dfrac{\epsilon_{In}}{\epsilon_P}  \dfrac{I_{\gamma,In}}{I_{\gamma,P}} \dfrac{e^{-\mu_{In}x_{In}/2}\times e^{-\mu_{In}x_{P}}}{e^{-\mu_{P}x_{P}/2}} \nonumber
\end{align}

@@

With the exception of decay constants, which are assumed to be exact, each of the parameters in this model carries statistical uncertainty in measurement. In lieu of a differential error propagation, the total statistical error $\delta_\sigma$ is taken as the quadrature sum of all of the other errors  $\delta_i$:

@@

XXXXXXXXXXXXXXXX

\comment{Not sure what else we need to consider for systematics...}

@@

Using the ratio methods described here, the cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been calculated for incident neutron energy of 2.7645 MeV,  + 0.0151 MeV / - 0.0219 MeV. These values are recorded in \autoref{tab:xs_results}.

@@

\comment{How many sig figs to round uncertainties to in table?}

\comment{Report all 3 values in table? Report a weighted average between them?}

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}
\centering
\caption{Results of cross section measurement. }
\label{tab:xs_results}
\begin{tabular}{@{}cc@{}}
\toprule
Reaction                                                                            & $\sigma$($E_n$ = 2.7645 MeV) (mb)                                                                       \\ \midrule
\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.953 $\pm$ 3.351, \\ 46.493 $\pm$ 2.805, \\ 46.9 $\pm$ 3.189\end{tabular}  \\
\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}49.716 $\pm$ 3.335, \\ 49.011 $\pm$ 2.698, \\ XXXX $\pm$ XXXXXX\end{tabular} \\
\begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.901 $\pm$ 1.7089, \\ XXXXX $\pm$ XXXXX\end{tabular}                   \\ \bottomrule
\end{tabular}
\end{table}

>>>>

After irradiation, the co-loaded targets were removed from the HFNG and transferred to a counting lab, where their induced activities could be measured via gamma ray spectroscopy. Two detectors were used in this measurement. An Ortec 80\% High-Purity Germanium (HPGe) detector was used for the detection of the positron annihilation radiation from the \ce{^{64}Cu}  decay, the 336 keV gamma-ray from the decay of the \ce{^{115m}In}  isomer and the 391 keV gamma-ray from the \ce{^{113m}In}  isomer. An Ortec planar Low-Energy Photon Spectrometer (LEPS)  was used for the detection of the lower-energy 159 keV gamma-ray from \ce{^{47}Sc} as well as the two indium isomers mentioned above. Both detectors were calibrated for energy and efficiency, using \ce{^{133}Ba}, \ce{^{137}Cs}, and \ce{^{152}Eu} sources at various distances from the front face of each detector. These efficiencies, along with gamma ray intensities for each transition, are used to convert the integrated counts in each gamma ray photopeak into an activity for the activated isotopes and isomeric states.

\comment{You should add a table listing the gamma-ray properties for the indium isomers and the 64Cu and 47Sc decay lines. This should include the proper NDS citation.}

% \begin{figure*}[H]
%     \centering
%     \begin{subfigure}[t]{0.7\textwidth}
%         \centering
% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \includegraphics[height=2.8in]{./figures/IMG_20160531_182618557_HDR.jpg}
%         \caption{ Ortec 80\% HPGe detector}
%         \label{fig:hpge_a}
%     \end{subfigure}%
%     ~ 
%     \begin{subfigure}[t]{0.28\textwidth}
%         \centering
% %         \includegraphics[width=\textwidth]{./figures/target2.png}
%         \includegraphics[height=2.8in]{./figures/IMG_20160531_182635712_HDR.jpg}
%         \caption{Ortec planar LEPS detector}
%                 \label{fig:hpge_b}
%     \end{subfigure}
%     \caption{High-Purity Germanium Detectors used for gamma spectroscopy of the activated foils.}
%      \label{fig:main_ge_detectors}
% \end{figure*}
% 
% \comment{Does \autoref{fig:main_ge_detectors} serve any purpose? Should it be cut?}

The foils were counted in their polyethylene holder, 10 cm from the front face of the 80\% HPGe and 1 cm from the front face of the LEPS, with the target foil (zinc or titanium) facing towards the front face of the detector when both target and monitor foils were counted simultaneously. All data collection was performed using the Ortec MAESTRO software. For each experiment the detector dead time was verified to be less than 5\%.  No summing corrections need to be made since all of the gammas are either non-coincident or formed in a back-to-back annihilation event. This was never an issue for any experiments, but had it been, the foils would be moved to a position of greater standoff from the detector.

For the  \ce{^{47}Sc} production experiments, the foils were counted simultaneously using a planar LEPS detector. For the \ce{^{64}Cu} production experiments, the Indium foil was first counted separately using an 80\% HPGe detector, to capture the short-lived Indium activities. This is due to the fact that the \ce{^{115}In}(n,$\gamma$) reaction results in the production of \ce{^{116}In} which has a 54 minute half-life and results in the production of 1097 keV (58.5\% branching), 1293 keV (84.8\% branching) and 2112 keV (15.09\% branching) gamma-rays that in turn produce a significant number of 511 keV gammas from pair-production followed by annihilation. The foils were counted together again after approximately 4 hours of separate collection, to allow for nearly all of the \ce{^{116}In} to decay. Example spectra for each production pathway can be seen in \autoref{fig:spectra_a} and \autoref{fig:spectra_b}.

\begin{figure*}[ht]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \includegraphics[width=5in]{./figures/ti_foils.png}
        \includegraphics[width=5in]{./figures/47sc_gspectrum_alt.pdf}
        \caption{ Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a LEPS detector}
        \label{fig:spectra_a}
    \end{subfigure}%
    \\
    \begin{subfigure}[t]{\textwidth}
        \centering
%         \includegraphics[width=\textwidth]{./figures/target2.png}
%         \includegraphics[width=5in]{./figures/Sample_spectra.png}
        \includegraphics[width=5in]{./figures/64Cu_gspectrum_alt.pdf}
        \caption{Gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
                \label{fig:spectra_b}
    \end{subfigure}
    \caption{Example gamma spectra collected to monitor radioisotope production.}
     \label{fig:main_spectra}
\end{figure*}

To verify that each peak corresponds to the assigned decay product, spectra were acquired in a sequence of 15 - 30 minute intervals. The resulting time series displayed in Figures \ref{fig:decay_curve_336} - \ref{fig:decay_curve_511} allow the fitting of exponential decay functions for each nuclide and comparison of the measured half-life with literature values. The fitted functions for each transition agree (at the 1$\sigma$ confidence level) with accepted half-lives \textcolor{red}{[XXXref reference original papers for the T1/2s]}, confirming the respective peak assignments.

\comment{Reference original ENSDF papers}

@@

The spectra for the different samples were summed and the peak area over background was determined using gf3, part of the RadWare analysis package from Oak Ridge   \cite{radford2000radware, Radford1995}. The background-subtracted integrated counts in each photopeak, as well as the counting duration for each experiment, are tabulated in \autoref{tab:peak_counts}.

@@

\subsection{Experimental verification of incident neutron energy}\label{sec:lee_sec}

As shown in \autoref{sec:sample_loading} above, the effective neutron energy depends on the angle range subtended by the sample with respect to the incident deuteron beam.  In order to determine this angle it is necessary to measure the lateral location of the beam with respect to the sample location.  This centroid of the beam was measured using a 3 x 3 array of 0.5 cm diameter indium foils.  The relative activity of these foils was then determined via post-irradiation counting of the \ce{^{115m}In} isomer ($t_{1/2}$ = 4.486 h).  \autoref{fig:in_heat_plot} below shows the measured activities for these 9 indium foils.  Based on these values we are able to verify that the beam was indeed centered on the middle of the zinc and titanium samples.

% 
% \begin{figure}
%  \centering
%  \includegraphics[scale=0.6]{./figures/XXX.pdf}
%  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
%  \caption{\textcolor{red}{INSERT CAPTION HERE}}
%  \label{fig:in_heat_plot}
% \end{figure}
%

\comment{cire relevant NDS article for t1/2}

\comment{CHECK WITH ERIC for 3x3 In info and plot}

@@

For a thin target consisting of \(N_T\) target nuclei (with a reaction cross section $\sigma\pp{\bar{E}}$), subjected to a constant neutron flux $\phi\pp{\bar{E}}$, the rate of production ($R$) of the product nucleus will be:

@@

If this irradiation lasts for  some time $t_1$, and gamma ray spectrum acquisition begins at a later time $t_2$ and ends at  $t_3$, then the number of product decays ($D$; with decay constant $\lambda$) during the acquisition will be:

\begin{equation}
\begin{aligned}
D &= \dfrac{R}{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_3} - e^{-\lambda t_2}}
\\
&= \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_3} - e^{-\lambda t_2}} 
\end{aligned}
\end{equation}

If this decay emits a gamma ray with branching ratio $I_\gamma$ (photons emitted per decay), and is detected with an absolute efficiency  of $\epsilon_\gamma$ (photons detected / photons emitted), then the number of observed decays between $t_2$ and $t_3$ will be:

@@

\begin{align}
N_{obs} &= D \epsilon_\gamma I_\gamma \\
&=  \epsilon_\gamma I_\gamma  \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_3} - e^{-\lambda t_2}} \nonumber
\end{align}

Solving this equation for the  cross-section results in:

\begin{equation}\label{eqn:single_xs_eqn}
\sigma\pp{\bar{E}} = \dfrac{N_{obs}\lambda}{N_T \epsilon_\gamma I_\gamma  \phi\pp{\bar{E}}  \pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_3} - e^{-\lambda t_2}}}
\end{equation}

\autoref{eqn:single_xs_eqn} can be used to determine the unknown (n,p) cross sections relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} inelastic scattering cross sections since the Zn and Ti samples were co-irradiated with indium foils. This approach has a number of advantages since the result is independent of neutron flux and only depends on the relative detector efficiencies at each gamma-ray energy.  \autoref{eqn:calc_eqn} shows the ratio of the cross sections determined using this approach, in which subscript $P$ indicates a quantity for either \ce{^{64}Cu} or \ce{^{47}Sc}, and subscript $In$ indicates a quantity for either the \ce{^{113m}In} or \ce{^{115m}In} isomer. A minor term was added to correct for the small self-attenuation of the gamma rays emitted by the activated foils:

\begin{align}\label{eqn:calc_eqn}
\dfrac{\sigma_P}{\sigma_{In}} &=  \dfrac{A_P}{A_{In}} \dfrac{N_{T,In}}{N_{T,P}} \dfrac{\lambda_P}{\lambda_{In}} \dfrac{e^{\lambda_{In}t_1}-1}{e^{\lambda_{P}t_1}-1}  \\
&\times \dfrac{e^{-\lambda_{In}t_3}-e^{-\lambda_{In}t_2}}{e^{-\lambda_{P}t_3} - e^{-\lambda_{P}t_2}} \dfrac{\epsilon_{In}}{\epsilon_P}  \dfrac{I_{\gamma,In}}{I_{\gamma,P}} \dfrac{e^{-\mu_{In}x_{In}/2}\times e^{-\mu_{In}x_{P}}}{e^{-\mu_{P}x_{P}/2}} \nonumber
\end{align}

@@

In addition to the \ce{^{115}In}(n,n')\ce{^{115m}In} reference cross section, the \ce{^{115}In}(n,$\gamma$)\ce{^{116m}In}  ($t_{1/2}$ = 54.29 min) activity can be used to determine the  \ce{^{64}Zn}(n,p) and \ce{^{47}Ti}(n,p) cross section.  The capture activity is potentially subject to contamination from lower energy, especially thermal, \enquote{room return} neutrons since the (n,$\gamma$) cross section at 25 meV is approximately YYY MeV greater than at 2.7 MeV.

\comment{cite relevant NDS article}

\comment{add appropriate numbers to (n,g) cross sections}

\comment{cite IRDFF somewhere?}

With the exception of decay constants, which have negligible uncertainty compared to other sources of uncertainties in this work, each of the parameters in this model carries a statistical uncertainty. Based on the assumption that these uncertainties are independent, the total relative statistical uncertainty $\delta_\sigma$ is calculated by taking the quadrature sum of the relative uncertainties of each parameter  $\delta_i$:

@@

The largest source of systematic uncertainty in the cross section determined via the \enquote{ratio approach} is the \textcolor{red}{YYY\%} uncertainty in the \ce{^{115}In}(n,n')\ce{^{115m}In}  cross section and the \textcolor{red}{YYY\%} uncertainty in the \ce{^{113}In}(n,n')\ce{^{113m}In}  cross section.  An additional uncertainty arises from the fact that the Zn/Ti samples are not located at exactly the same location as the indium monitor foils, and are therefore not subject to precisely the same neutron flux.  However, the MCNP6 simulations shown in \autoref{fig:mcnp_flux} indicate that the difference in the flux that the two foils are subjected to is less than \textcolor{red}{YY\%}.  Other monitor foils could be used instead of indium, with \ce{^{57}Ni}(n,p)\ce{^{57}Co} being one possible candidate, but the 4.486 hour and 99.476 minute half-lives of the \ce{^{115m}In} and \ce{^{113m}In} isomers \textcolor{red}{[XXXref NDS]}, respectively, makes indium a better candidate for measuring the production of radionuclides with lifetimes much less than 77+ days. The largest source of uncertainty in energy window arises from uncertainties in the actual dimension of the deuteron beam on the production target.  We believe, based on \enquote{burn marks} on the production target that the beam was approximately circular, with a flat intensity profile and a 5 mm diameter.  However, every 1 mm change in the beam radius would cause a \textcolor{red}{XXX} MeV shift in the centroid and a \textcolor{red}{YYY} MeV change in the effective energy bin.

\comment{filling in missing data}

\comment{Use your energy-angle figure from Lisken above to estimate these numbers. You can point to the figure in the text if you'd like.}

@@

Using the ratio method described here, the cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been calculated for incident neutron energy of 2.7645 MeV,  + 0.0151 MeV / - 0.0219 MeV. These values are recorded in \autoref{tab:xs_results}.

@@

\comment{Truncate sig figs here - Note that the systematic uncertainty you calculated in the previous paragraph will provide a natural limit on the number of significant figures you quote for the energy window.}

\comment{Report a weighted average between the solo values, insert in text}

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}
\centering
\caption{Results of cross section measurement. Note that the last data point for the \ce{^{47}Sc} measurement (marked with *) was performed at a slightly different beam spot location, leading to a difference in effective neutron energy.}
\label{tab:xs_results}
\begin{tabular}{@{}cc@{}}
\toprule
Reaction                                                                            & $\sigma$($E_n$ = 2.7645 MeV) (mb)                                                                       \\ \midrule
\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.953 $\pm$ 3.351, \\ 46.493 $\pm$ 2.805, \\ 46.9 $\pm$ 3.189\end{tabular}  \\
\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}49.716 $\pm$ 3.335, \\ 49.011 $\pm$ 2.698, \\ XXXX $\pm$ XXXXXX\end{tabular} \\
\begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.901 $\pm$ 1.7089, \\ XXXXX $\pm$ XXXXX\end{tabular}                   \\ \bottomrule
\end{tabular}
\end{table}

\comment{Truncate sig figs in En in \autoref{tab:xs_results} }
